### 2019-04-02 1_introduction.tex
A few more small edits and rewording to deal with some passive voice.

There is another, deeper issue with TPS. TPS may be measured with
empty tasks~\cite{LegionTracing18} or with tasks of some
duration~\cite{Canary16, Armstrong14}. If empty tasks are used, the
resulting upper bound on task scheduling throughput fails to represent
any realistic application, as no
useful work is being performed. If non-empty tasks are used, \emph{but
  the efficiency of the overall application is not reported}, then TPS
is not a measurement of runtime-limited performance. Large tasks may
be used to hide any amount of runtime overhead,
while tasks that are too small may result in a drop in total
application throughput even as TPS increases. Only by constraining
efficiency, as in METG, can we meaningfully measure how runtime
overhead impacts the ability perform useful application work.

>>>>

There is another, deeper issue with TPS. TPS may be measured with
empty tasks~\cite{LegionTracing18} or with tasks of some
duration~\cite{Canary16, Armstrong14}. When using empty tasks, the
resulting upper bound on task scheduling throughput fails to represent
useful work within a realistic application. With non-empty tasks,
\emph{where the efficiency of the overall application is not
 reported}, TPS is not a measurement of runtime-limited
performance. Large tasks may be used to hide any amount of runtime
overhead, while tasks that are too small may result in a drop in total
application throughput even as TPS increases. Only by constraining
efficiency, as in METG, can we meaningfully measure how runtime
overhead impacts the ability to perform useful application work.
